Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-11-12 paper/paper.tex
fix conclusion
pending commit

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accommodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suites exist for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests constantly fail on the
most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

@@

\vspace{1ex}
\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows the
number of bug reports found per engine (\ref{fig:stacked-engine}) and
technique (\ref{fig:stacked-technique}). Each stacked bar breaks down
the bugs per status (\eg{}, ``1-New''). The prefix number serves to
indicate the ordering that status labels are assigned. Note that
several of these reports have the label ``3-Fixed'', indicating that
bug fixes have been incorporated into the code already.\Comment{
  Depending on the issue date, the fix may be in the latest release of
  the corresponding engines.} Overall, discarding bug reports with the
``1-New'' status, we reported a total of \totalBugsConfirmed{}
bugs. We found that the vast majority of bug reports targeted the engines
from Microsoft and Apple. Considering the techniques, the number of
bug reports were similar, if we consider only those confirmed or
fixed. Most of these bugs are of moderate severity. All in all, these
simple techniques seem promising to improve reliability of engines
that continuously evolve with their specifications.

%% We found,
%% however, that the cost of inspecting \Fix{...elaborate...}
%% It is
%% also worth noting that several of these reports hold the status
%% ``new'', which indicates that they were not reviewed yet by the
%% development team. Note also that we did not find bugs in the Mozilla
%% \smonkey\ engine.

@@

This code snippet was obtained by fuzzing a Test262 test with
\quickfuzz. In its original version, a string (omitted for space),
passed as argument to the \CodeIn{eval} function, encoded the actual
test. The fuzzer replaced the string argument with a function whose
body is a \CodeIn{break} statement outside a valid block
statement. Section B.3.3.3 from the spec~\cite{spec-b333} documents
how eval should be handle code containing a function declaration.
According to specification~\cite{break-statement}, the break statement
should throw an early error--in this case a SyntaxError--if the break
statement is not nested in an iterable or a switch statement. In
this case, all engines behave as expected but \veight{} pass without
failures.

@@

Overall, we reported \totalBugsReported\ bugs in this study. Of which,
\totalBugsConfirmed\ were confirmed by developers and
\totalBugsConfirmed\ were fixed. Although more work is necessary to
reduce cost of manual analysis, we found that both techniques we used
are effective at finding bugs in
\js\ engines. Section~\ref{sec:lessons} elaborates on the lessons
learned from this study. The result data, infrastructure, and
experimental scripts we prepared to run this study are available upon
request. Future work includes mining test inputs from alternative
sources (\eg{}, bug trackers) and predicting likelihood of false
positives as to guide human effort on the most promising warnings
first.

>>>>

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accommodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suite exists for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests constantly fail on the
most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

@@

\vspace{1ex}
\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows the
breakdown of bug reports found per engine (\ref{fig:stacked-engine})
and technique (\ref{fig:stacked-technique}). Each stacked bar breaks
down the bugs per status (\eg{}, ``1-New'', ``2-Confirmed'',
etc.). The prefix number indicates the ordering that status labels are
assigned. Note that several of these reports have the label
``3-Fixed'', indicating that bug fixes have been incorporated into the
code already.\Comment{ Depending on the issue date, the fix may be in
  the latest release of the corresponding engines.} Overall, ignoring
bug reports with the ``1-New'' status, we reported a total of
\totalBugsConfirmed{} bugs. We found that the vast majority of bug
reports targeted the engines from Microsoft and Apple. Considering the
techniques, the number of bug reports were similar, if we consider
only those confirmed or fixed. Most of these bugs are of moderate
severity. All in all, these simple techniques seem promising to
improve reliability of engines that continuously evolve with their
specifications.

@@

This code snippet was obtained by fuzzing a Test262 test with
\quickfuzz. In its original version, a string (omitted for space),
passed as argument to the \CodeIn{eval} function, encoded the actual
test. The fuzzer replaced the string argument with a function whose
body is a \CodeIn{break} statement outside a valid block
statement. Section B.3.3.3 from the spec~\cite{spec-b333} documents
how eval should handle code containing function declarations.
According to the spec~\cite{break-statement}, the virtual machine
should throw an early error--in this case, a SyntaxError--if the break
statement is not nested in an iterable or a switch statement. In this
case, all engines, but \veight{}, behave as expected.

@@

Overall, we reported \totalBugsReported\ bugs in this study. Of which,
\totalBugsConfirmed\ were confirmed by developers and
\totalBugsFixed\ were fixed. Although more work is necessary to
reduce cost of manual analysis, we found that both techniques we used
are effective at finding bugs in
\js\ engines. Section~\ref{sec:lessons} elaborates on the lessons
learned from this study. The result data, infrastructure, and
experimental scripts we prepared to run this study are available upon
request. Future work includes mining test inputs from alternative
sources (\eg{}, bug trackers) and predicting likelihood of false
positives as to guide human effort on the most promising warnings
first.
